First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-05-26 ms.tex
Updated upper limit table, this time with correct values

\begin{deluxetable}{ccccccc}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
\tablewidth{\columnwidth}
\tablecaption{Upper limits on the EoR power spectrum for our three 
sub-bands and two polarizations. Upper limits, $\Delta^2_{\text{UL}}$, are at 97.7\% 
confidence level. Cosmological wavenumbers, $k$, are in units of h~Mpc$^{-1}$ and upper limits are in units of mK$^2$. The last two columns, RTS-CHIPS, are produced from the reference pipeline which is discussed in Section~\ref{subsec:ref_pipe}.
\label{tbl:limits}
}
\tablehead{
& & & \multicolumn{2}{c}{FHD-\eppsilon} & \multicolumn{2}{c}{RTS-CHIPS} \\
Sub-band & $z_0$ & Pol & $k$  & $\Delta^2_{\text{UL}}$ & $k$ & $\Delta^2_{\text{UL}}$
}
\startdata
Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$ & &\\
Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.12 & 2.5 $\times 10^4$ \\
Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$ & &\\
Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.14 & 2.2 $\times 10^4$ \\
High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$ & &\\
High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.12 & 2.3 $\times 10^4$ \\
\enddata
\end{deluxetable}

>>>>

\begin{deluxetable}{ccccccc}
\tabletypesize{\footnotesize}
%\tablecolumns{7}
\tablewidth{\columnwidth}
\tablecaption{Upper limits on the EoR power spectrum for our three 
sub-bands and two polarizations. Upper limits, $\Delta^2_{\text{UL}}$, are at 97.7\% 
confidence level. Cosmological wavenumbers, $k$, are in units of h~Mpc$^{-1}$ and upper limits are in units of mK$^2$. The last two columns, RTS-CHIPS, are produced from the reference pipeline which is discussed in Section~\ref{subsec:ref_pipe}.
\label{tbl:limits}
}
\tablehead{
& & & \multicolumn{2}{c}{FHD-\eppsilon} & \multicolumn{2}{c}{RTS-CHIPS} \\
Sub-band & $z_0$ & Pol & $k$  & $\Delta^2_{\text{UL}}$ & $k$ & $\Delta^2_{\text{UL}}$
}
\startdata
Low & 7.1 & E-W & 0.231 & 3.67 $\times 10^4$ & &\\
Low & 7.1 & N-S & 0.27 & 2.70 $\times 10^4$ & 0.16 & 3.2 $\times 10^4$ \\
Mid & 6.8 & E-W & 0.24 & 3.56 $\times 10^4$ & &\\
Mid & 6.8 & N-S & 0.24 & 3.02 $\times 10^4$ & 0.14 & 2.6 $\times 10^4$ \\
High & 6.5 & E-W & 0.20 & 4.70 $\times 10^4$ & &\\
High & 6.5 & N-S & 0.24 & 3.22 $\times 10^4$ & 0.14 & 2.5 $\times 10^4$ \\
\enddata
\end{deluxetable}
